---
title: "Untitled"
output: html_document
date: "2026-02-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}

library(here)
library(tidyverse)

```

```{r}

all_overall <- read.csv(here("data", "overall_mrp_preds_all.csv"))

age_overall <- read.csv(here("data", "age_mrp_preds_all.csv"))

education_overall <- read.csv(here("data", "degree_mrp_preds_all.csv"))

ethnicity_overall <- read.csv(here("data", "ethnicity_mrp_preds_all.csv"))

sex_overall <- read.csv(here("data", "sex_mrp_preds_all.csv"))

housing_overall <- read.csv(here("data", "housing_mrp_preds_all.csv"))


all_overall_1 <- all_overall %>%
  mutate(
    across(c(Conservative, Left, Other, Reform.UK, WNV), ~ .x * 100),
    row_total = Conservative + Left + Other + Reform.UK + WNV
  )


age_overall_1 <- age_overall %>%
  mutate(
    across(c(Conservative, Left, Other, Reform.UK, WNV), ~ .x * 100),
    row_total = Conservative + Left + Other + Reform.UK + WNV
  )
 
  

  
education_overall_1 <- education_overall %>% 
 mutate(
    across(c(Conservative, Left, Other, Reform.UK, WNV), ~ .x * 100),
    row_total = Conservative + Left + Other + Reform.UK + WNV
  )
 
  
sex_overall_1 <- sex_overall %>% 
 mutate(
    across(c(Conservative, Left, Other, Reform.UK, WNV), ~ .x * 100),
    row_total = Conservative + Left + Other + Reform.UK + WNV
  )
  
  
ethnicity_overall_1 <- ethnicity_overall %>% 
  mutate(
    across(c(Conservative, Left, Other, Reform.UK, WNV), ~ .x * 100),
    row_total = Conservative + Left + Other + Reform.UK + WNV
  )
  

  

  
  
  
housing_overall_1 <- housing_overall %>% 
    mutate(
    across(c(Conservative, Left, Other, Reform.UK, WNV), ~ .x * 100),
    row_total = Conservative + Left + Other + Reform.UK + WNV
  )
    
  
  
  
  
write.csv(all_overall_1, here("output", "all_overall_1.csv"), row.names = FALSE)
  

write.csv(age_overall_1, here("output", "age_overall_1.csv"), row.names = FALSE)


write.csv(education_overall_1, here("output", "education_overall_1.csv"), row.names = FALSE)

write.csv(ethnicity_overall_1, here("output", "ethnicity_overall_1.csv"), row.names = FALSE)


write.csv(housing_overall_1, here("output", "housing_overall_1.csv"), row.names = FALSE)

```






```{r}

overall_results_normalized <- all_overall %>%
  mutate(
    row_total = rowSums(select(., Conservative:WNV)),
    across(
      c(Conservative, Left, Other, Reform.UK, WNV),
      ~ .x / row_total * 100,
      .names = "{.col}_normalized"
    )
  ) %>%
  select(const_name, ends_with("_normalized"))



sex_results_normalized <- sex_overall %>%
  mutate(
    row_total = rowSums(select(., Conservative:WNV)),
    across(
      c(Conservative, Left, Other, Reform.UK, WNV),
      ~ .x / row_total * 100,
      .names = "{.col}_normalized"
    )
  ) %>%
  select(const_name, sex_level, ends_with("_normalized"))





edu_results_normalized <- education_overall %>%
  mutate(
    row_total = rowSums(select(., Conservative:WNV)),
    across(
      c(Conservative, Left, Other, Reform.UK, WNV),
      ~ .x / row_total * 100,
      .names = "{.col}_normalized"
    )
  ) %>%
  select(const_name, edu_level, ends_with("_normalized"))



ethnicity_results_normalized <- ethnicity_overall %>%
  mutate(
    row_total = rowSums(select(., Conservative:WNV)),
    across(
      c(Conservative, Left, Other, Reform.UK, WNV),
      ~ .x / row_total * 100,
      .names = "{.col}_normalized"
    )
  ) %>%
  select(const_name, ethn_level, ends_with("_normalized"))






age_results_normalized <- age_overall %>%
  mutate(
    row_total = rowSums(select(., Conservative:WNV)),
    across(
      c(Conservative, Left, Other, Reform.UK, WNV),
      ~ .x / row_total * 100,
      .names = "{.col}_normalized"
    )
  ) %>%
  select(const_name, age_level, ends_with("_normalized"))



housing_results_normalized <- housing_overall %>%
  mutate(
    row_total = rowSums(select(., Conservative:WNV)),
    across(
      c(Conservative, Left, Other, Reform.UK, WNV),
      ~ .x / row_total * 100,
      .names = "{.col}_normalized"
    )
  ) %>%
  select(const_name, housing, ends_with("_normalized"))




  
write.csv(overall_results_normalized, here("output", "overall_results_normalized.csv"), row.names = FALSE)
  

write.csv(age_results_normalized, here("output", "age_results_normalized.csv"), row.names = FALSE)


write.csv(edu_results_normalized, here("output", "edu_reults_normalized.csv"), row.names = FALSE)

write.csv(ethnicity_results_normalized, here("output", "ethnicity_results_normalized.csv"), row.names = FALSE)


write.csv(housing_results_normalized, here("output", "housing_results_normalized.csv"), row.names = FALSE)





